Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7

### 2019-07-22 paper/ms.tex
paper: add detrended lc plot

>>>>

\begin{figure}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.47\textwidth]{detrended_light_curves_sec6cam1ccd1.pdf}
	\end{center}
	\vspace{-0.5cm}
	\caption{
    Twenty randomly selected light curves drawn
    from the same sector, camera,
    and CCD, for stars with $T$-band magnitudes between 13 and 14.
    Each light curve is shown from top to bottom in raw, PCA-detrended, and
    TFA-detrended forms.
    Stellar rotation signals are usually preserved in the PCA light curves,
    while TFA tends to either filter them out, or to distort them.
		\label{fig:detrended}
	}
\end{figure}
